---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nyankomicro

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

nyankomicro is a in-house package that aims to make the plots more beautiful.

The barplots created by various packages force annotations when the annotation for a particular domain is unknown (e.g., NA, uncultured, uncultured bacterium, etc.), which confuses the discussion. To avoid these confusions, this package uniquely sets unknown annotations as Undetermined. It will also show the taxonomy to be displayed if it is N% or more in at least one sample.

## Installation

You can install the released version of demopckg from [GitHub](https://github.com) with:

``` r
devtools::install_github("xvtyzn/nyankomicro")
```

``` r
devtools::update_packages("nyankomicro")
```

## Example

### Barplot

```{r example1, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
library(phyloseq)
library(nyankomicro)
data("GlobalPatterns")

microbiome_barplot(GlobalPatterns, "Order", "SampleType", 10)
```

Following the naming conventions for bacteria, italics are used to classify bacteria below the family level.

```{r example1 family level, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
microbiome_barplot(GlobalPatterns, "Family", "SampleType", 10)
```

### DEseq2 plot

```{r example2, fig.height=6, fig.width=12, message=FALSE, warning=FALSE}
library(DESeq2)
library(tidyverse)

subGP <- subset_samples(GlobalPatterns, SampleType %in% c("Skin", "Tongue") )
  
deseq2_subGP <- subGP %>%
  phyloseq_to_deseq2(~SampleType) %>%
  DESeq() %>%
  results(cooksCutoff = FALSE)

ggtree_subGP <- deseq2_tree(subGP, deseq2_subGP,level = "Phylum", alpha = 0.01,
                            sample_annotation = "SampleType")
ggtree_subGP
```

### Core microbiome estimation

コアmicrobiomeの決定には複数の議論が存在します。

```{r example3, fig.height=12, fig.width=6, message=FALSE, warning=FALSE}

```
